---
title: "KNN Notebook"
output: html_notebook
---

K-Nearest Neighbor Algorithm

Install packages to run kNN
```{r}
library(class)
```
Creating a dataset
```{r}
new <- c(0.05,0.25)
A <- c(0.0467,0.2471)
B <- c(0.0533,0.1912)
C <- c(0.0917,0.2794)
data <-rbind(A,B,C)
dimnames(data) <- list(c("Dark","Medium","Medium"),c("Age (MMN)", "Na/K (MMN)"))
#Declare true classification of A, B and C.
trueclass <-c("Dark","Medium","Medium")
```
Run kNN
```{r}
knn(data,new,cl=trueclass,k=3,prob = TRUE)
```
#Calculate the Euclidean Distance
```{r}
install.packages("fields")
library(fields)
together <- rbind(new,data)
#The top row of the rdist are the distance values from the New rdist(together)
rdist(together)
```
```{r}
#Stretch the axes
ds_newA <- sqrt((new[1]-A[1])^2 +(3*(new[2]-A[2]))^2)
ds_newB <- sqrt((new[1]-B[1])^2 +(3*(new[2]-B[2]))^2)
ds_newC <- sqrt((new[1]-C[1])^2 +(3*(new[2]-C[2]))^2)

```

```{r}
distance<-c(ds_newA,ds_newB,ds_newC)
BP<-c(120,122,130)
data<-cbind(BP,data,distance)
data
```

```{r}
#Weights-inverse of distance
weights<-(1/(distance)^2)
sum_wi<-sum(weights)
sum_wiyi<-sum(weights*data[,1])
yhat_new<-sum_wiyi/sum_wi
yhat_new
```

Notes : Regarding kNN

k-Nearest Neighbour Classification

Description

k-nearest neighbour classification for test set from training set. For each row of the test set, the k nearest (in Euclidean distance) training set vectors are found, and the classification is decided by majority vote, with ties broken at random. If there are ties for the kth nearest vector, all candidates are included in the vote.

Usage

knn(train, test, cl, k = 1, l = 0, prob = FALSE, use.all = TRUE)
Arguments

train	
matrix or data frame of training set cases.
test	
matrix or data frame of test set cases. A vector will be interpreted as a row vector for a single case.
cl	
factor of true classifications of training set
k	
number of neighbours considered.
l	
minimum vote for definite decision, otherwise doubt. (More precisely, less than k-l dissenting votes are allowed, even if k is increased by ties.)
prob	
If this is true, the proportion of the votes for the winning class are returned as attribute prob.
use.all	
controls handling of ties. If true, all distances equal to the kth largest are included. If false, a random selection of distances equal to the kth is chosen to use exactly k neighbours.